CNNNano --- MinION basecaller pogonjen dubokim ucenjem

### 2017-04-29 paper/main.tex
Added method beginning

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\chapter{Results}

>>>>

Instead of opting for traditional path using HMM or RNN we tried using CNN~(Convolutional neural networks)~\cite{lecun-98}, that is their residual version~\cite{he2016deep}. We opted out for gated residuan network variant~\cite{savarese2016learning}. For loss we used CTC (Connectionist temporal classification)~\cite{graves2006connectionist} between basecallled and target sequence. The implementation used is open source warp-ctc~\cite{warpctc}. Main computation framework is tensorflow~\cite{tensorflow2015-whitepaper}

\section{Data preprocessing}

\chapter{Results}
